### 2021-06-07 paper/report.tex
Add Science reference by Lessler.

At the core of our agent-based model are physical contacts between heterogeneous agents
(Figure~\ref{fig:broad_model_description}).\footnote{We provide a detailed comparison to
other approaches in \ref{sec:literature_review}. The model most closely related to ours
is described in \citet{Hinch2020}.} Each contact between an infectious individual and
somebody susceptible to the disease bears the risk of transmitting the virus. Contacts
occur in the household, at work, at school, or in other settings (leisure activities,
grocery shopping, medical appointments, etc.).\comment[id=HM]{Systemic relevance of
work?} Some contacts recur regularly, others occur at random. Random contacts are
typically assortative in age and geographical location. Empirical applications can take
the population structure from census data and the types and frequency of contacts from
diary data measuring contacts before the pandemic
\citep[e.g.][]{Mossong2008}.\footnote{\citet{Hoang2019} provide access to multiple data
sets on contact types and frequencies at \url{http://www.socialcontactdata.org/} covering
countries from all continents except North America and Australia.} The dimensions are
chosen so that the most common NPIs can be modeled in great detail by reducing the number
of contacts in a particular setting or the risk of transmitting the disease for a type of
contact. For example, a mandate to work from home will reduce the number of work contacts
to zero for a fraction of the working population. Schools and daycare can be closed
entirely, operate at reduced capacity including an alternating schedule, or implement
mitigation measures like masking requirements or air filters.\comment[id=HM]{cite
\url{https://science.sciencemag.org/content/early/2021/04/28/science.abh2939}} Curfews
may reduce the number of contacts in non-work/non-school settings. In any setting,
measures like masking requirements would reduce the probability of infection associated
with a contact.

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the
period mid-September 2020 to the end of May 2020. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) and some data was not recorded
yet.\comment[id=HM]{True?}\comment[id=Klara]{We would definitely need to model national
and international travel which you mention below. Regarding data I think everything would
be available. The low numbers during summer in our sample size might also be a problem
because Covid might go extinct in our model when case numbers are so low.}. Second, a
large fraction cases during summer of 2020 were traced to international
travel,\comment[id=HM]{citation?}\comment[id=Klara]{There was a comment by minister Spahn
that half of cases during the summer months were due to travel to the Baltic
(\url{https://twitter.com/krstorevic/status/1396516025181556737}) but I know of no data.
We should probably check the RKI reports of July, Aug and Sep}, but the precise number is difficult to model.

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and
of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially
recorded cases; the \replaced[id=HM]{color}{blue?} line in
Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index\cite{Hale2020},
which tracks the tightness of non-pharmaceutical interventions. We transform the index so
that lower values represent higher levels of restrictions. A value of zero means all
measures incorporated in the index are turned on. The value 1 represents the situation of
mid-September, where half of all restrictions incorporated in the index are
active.\comment[id=HM]{Need to find version of index with a couple of measures, probably
need the API access...}. In the six weeks between mid September and mid October, cases
increased by a factor of \replaced[id=HM]{X}{10? Do we have RKI numbers as table
somewhere?}. Restrictions were somewhat tightened in mid-October and again in early
November. New infections remained constant throughout November, before rising again in
December.

>>>>

At the core of our agent-based model are physical contacts between heterogeneous agents
(Figure~\ref{fig:broad_model_description}).\footnote{We provide a detailed comparison to
other approaches in \ref{sec:literature_review}. The model most closely related to ours
is described in \citet{Hinch2020}.} Each contact between an infectious individual and
somebody susceptible to the disease bears the risk of transmitting the virus. Contacts
occur in the household, at work, at school, or in other settings (leisure activities,
grocery shopping, medical appointments, etc.).\comment[id=HM]{Systemic relevance of
work?} Some contacts recur regularly, others occur at random. Random contacts are
typically assortative in age and geographical location. Empirical applications can take
the population structure from census data and the types and frequency of contacts from
diary data measuring contacts before the pandemic
\citep[e.g.][]{Mossong2008}.\footnote{\citet{Hoang2019} provide access to multiple data
sets on contact types and frequencies at \url{http://www.socialcontactdata.org/} covering
countries from all continents except North America and Australia.} The dimensions are
chosen so that the most common NPIs can be modeled in great detail by reducing the number
of contacts in a particular setting or the risk of transmitting the disease for a type of
contact. For example, a mandate to work from home will reduce the number of work contacts
to zero for a fraction of the working population. Schools and daycare can be closed
entirely, operate at reduced capacity including an alternating schedule, or implement
mitigation measures like masking requirements or air filters \citep{Lessler2021}. Curfews
may reduce the number of contacts in non-work/non-school settings. In any setting,
measures like masking requirements would reduce the probability of infection associated
with a contact.

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the
period mid-September 2020 to the end of May 2020. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) and some data was not recorded
yet.\comment[id=HM]{True?}\comment[id=K]{We would definitely need to model national
and international travel which you mention below. Regarding data I think everything would
be available. The low numbers during summer in our sample size might also be a problem
because Covid might go extinct in our model when case numbers are so low.}. Second, a
large fraction cases during summer of 2020 were traced to international
travel,\comment[id=HM]{citation?}\comment[id=Klara]{There was a comment by minister Spahn
that half of cases during the summer months were due to travel to the Baltic
(\url{https://twitter.com/krstorevic/status/1396516025181556737}) but I know of no data.
We should probably check the RKI reports of July, Aug and Sep}, but the precise number is difficult to model.

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and
of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially
recorded cases; the \replaced[id=HM]{color}{blue?} line in
Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index \citep{Hale2020},
which tracks the tightness of non-pharmaceutical interventions. We transform the index so
that lower values represent higher levels of restrictions. A value of zero means all
measures incorporated in the index are turned on. The value 1 represents the situation of
mid-September, where half of all restrictions incorporated in the index are
active.\comment[id=HM]{Need to find version of index with a couple of measures, probably
need the API access...}. In the six weeks between mid September and mid October, cases
increased by a factor of \replaced[id=HM]{X}{10? Do we have RKI numbers as table
somewhere?}. Restrictions were somewhat tightened in mid-October and again in early
November. New infections remained constant throughout November, before rising again in
December.
